Inferring the effective start dates of non-pharmaceutical interventions during \covid outbreaks

### 2020-07-09 ms/ms.tex
added arrows to ppc

\section*{References}
\nolinenumbers
\bibliographystyle{agsm}
\bibliography{/Users/yoavram/Documents/library}
%\bibliography{ms}

@@

    Circles and stars represent daily case data up to and after Apr~11, 2020, respectively, and the vertical dashed line represents Apr~11.
    Black lines represents a smoothing of the data points using a Savitzky-Golay filter. 
    Colored lines represent posterior predictions from a model with fixed $\tau$ -- blue -- and free $\tau$ -- green. Models were fitted with data up to Apr~11. The predictions are generated by drawing 1,000 parameters sets from the posterior distribution, and then generating a daily case count using the SEIR model in \autoref{eq:model}. Note the differences in the y-axis scale.

>>>>

\section*{References}
\nolinenumbers
\bibliographystyle{agsm}
%\bibliography{/Users/yoavram/Documents/library}
\bibliography{ms}

@@

    The vertical dashed line represents Apr~11, 2020.
    Circles and stars represent daily case data up to and after Apr~11, respectively
    Black and white arrows denote the official $\tau^*$ and effective $\hat{\tau}$ start of NPIs, respectively.
    Black lines represent a smoothing of the data points using a Savitzky-Golay filter. 
    Coloured lines represent posterior predictions from a model with fixed $\tau$ (blue) and free $\tau$ (green). Models were fitted with data up to Apr~11. The predictions are generated by drawing 1,000 parameters sets from the posterior distribution, and then generating a daily case count using the SEIR model up to Apr~24. Note the differences in the y-axis scale.
